Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 main.tex
improved acknowledgements

I would like to thank all of my research group members, past and present, Stephanie Schieffer, Benjamin Rickman, John Hogan, Tuo Li, Daniel Brajkovic, Michael Greco, Michael Szotec, %TODO sp?
and Robin. %TODO last name!
I also want to thank former member Nathan Rimmington %TODO sp!
for laying the groundwork for the presented laser.
Through your professional efforts and personal interactions, you have made my time at UIC most enjoyable.

I want to thank my collaborators, Nigel Browning, %TODO argonne FIB guys,

>>>>

I would like to thank all of my research group members, past and present, Stephanie Schieffer, Benjamin Rickman, John Hogan, Tuo Li, Daniel Brajkovic, Michael Greco, Michael Szotek, and Robin Taylor.
Through your professional efforts and personal interactions, you have made my time at UIC most enjoyable.
I also want to thank former member Nathan Rimington for laying the groundwork for the presented laser.

I want to thank my collaborators, Nigel Browning, now of Pacific Nortwest National Laboratory, and Dean Miller and Jon Hiller of the Electron Microscopy Center at Argonne National Laboratory.
